\documentclass{article}
% Comment the following line to NOT allow the usage of umlauts
\usepackage[utf8]{inputenc}
% Uncomment the following line to allow the usage of graphics (.png, .jpg)
%\usepackage{graphicx}

\title{Latex Certificate Course Instructions}
\author{Jacob Antony}
\date{\today}

\begin{document}

\maketitle

\section*{Instructions}
\begin{enumerate}
	\item Open day04.tex using Verbtex
	\begin{enumerate}
		\item Download Daily Course Material and Assignment Instructions for Day 4 (day04.tex, asg04.pdf) from Google Classroom.
		\item Open Internal storage/Android/data/verbosus.verbtex/files/Local/Latex Course/ Folder using File Manger Application.
		\item Delete all files in ../Latex Course/ Folder.
		\item Copy day04.tex file into Internal storage/Android/data/verbosus.verbtex/files/Local/Latex Course/  Folder.
		\item Open Verbtex Application.
	\end{enumerate}
	\item Exercise
	\begin{enumerate}
		\item Add another item at the end of enumerated list, called ``Fourth item''
		\item Add footnote ``Assignment Day 4'' to the ``Fourth item''
		\item Save day04.tex and Generate pdf.
	\end{enumerate}
	\item Upload day04.tex, and Latex Course.pdf files into Google Classroom as your response to the assignment.
\end{enumerate}

\section{\LaTeX{} Concepts}

\subsection{\LaTeX{} Environments}
\begin{itemize}
	\item Environment \texttt{env} begins with \textbackslash{}begin\{\texttt{env}\} Command.\\ For example : \textbackslash{}begin\{document\}
	\item Environment \texttt{env} ends with  \textbackslash{}end\{\texttt{env}\} Command.\\ For example : \textbackslash{}end\{document\}
\end{itemize}

\subsection{List Environments}
\begin{itemize}
	\item There are three list environments : itemize, enumerate, description
	\item \textbackslash{}begin\{itemize\} \textbackslash{}item \dots \textbackslash{}end\{itemize\}
	\item \textbackslash{}begin\{enumerate\} \textbackslash{}item \dots \textbackslash{}end\{enumerate\}
	\item \textbackslash{}begin\{description\} \textbackslash{}item[\texttt{label}] \dots \textbackslash{}end\{description\}
\end{itemize}

\subsection*{Nested Environments}
\begin{itemize}
	\item Inner environments should be ended before ending outer environments.
\end{itemize}

\section{Bonus Material}
\begin{itemize}
	\item Try creating an enumerated list inside a bulleted list.
	\item Try creating an enumerated list inside another enumerated list.
	\item Try changing the bullet symbol of a bulleted list.
	\item Try changing the numbering style of an enumerated list into roman.
	\item Visit https://tex.stackexchange.com : \LaTeX{} Stackexchange Community
	\item Visit https://tug.org : \TeX{} User's Group
\end{itemize}


% Uncomment the following two lines if you want to have a bibliography
%\bibliographystyle{alpha}
%\bibliography{document}

\end{document}
