\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Latex Certificate Course Instructions}
\author{Jacob Antony}
\date{\today}

\begin{document}

\maketitle

\section*{Instructions}
\begin{enumerate}
	\item Open day05.tex using Verbtex
	\begin{enumerate}
		\item Download Daily Course Material and Assignment Instructions for Day 5 (day05.tex, asg05.pdf) from Google Classroom.
		\item Open Internal storage/Android/data/verbosus.verbtex/files/Local/Latex Course/ Folder using File Manger Application.
		\item Delete all files in ../Latex Course/ Folder.
		\item Copy day05.tex file into Internal storage/Android/data/verbosus.verbtex/files/Local/Latex Course/  Folder.
		\item Open Verbtex Application.
	\end{enumerate}
	\item Exercise
	\begin{enumerate}
		\item Set left margin 1.5 inches, right margin , top margin 1 inches and bottom margin 0.5 inches.
		\item Print date of document creation into left footer using \textbackslash{}today, \textbackslash{}lfoot Commands.
	\end{enumerate}
	\item Upload day05.tex, and Latex Course.pdf files into Google Classroom as your response to the assignment.
\end{enumerate}

\section{\LaTeX{} Concepts}

\subsection{\LaTeX{} Packages}
\begin{itemize}
	\item Packages provide additional features. \\ For example : enumitem
	\item enumitem : list styles customization, \dots
	\item fancyhdr : header \& footer customization, \dots
	\item geometry : page margin customization, \dots
\end{itemize}

\section*{Bonus Material}
\begin{itemize}
	\item Visit https://ctan.org : Documentation on \LaTeX{} Packages
\end{itemize}

\end{document}
